Funding programmes for early career researchers do/not influence their independence

### 2023-07-25 _targets.Rmd
final adjustements, added number of coauthors to the matching data

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych",
                            "arrow",
                            "tarchetypes",
                            "cobalt"
                            ))

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych",
                            "arrow",
                            "tarchetypes",
                            "cobalt",
                            "furrr"
                            ))

### 2023-07-25 article.Rmd
final adjustements, added number of coauthors to the matching data

However, we have made some changes to the indicator. After consulting with its authors, we have changed the aggregation formula to RII = ((1- I1) + I2 + I3 + I4) / 4, since the previous formula had a small error (it weighted I4 double,, i.e. 2*I4). For calculating the share of own research topics of the researcher (I4), we have also not used bibliographic coupling as originally suggested, but text-based topic modelling using publication titles and abstracts. Finally, the original indicator, while tracking not only collaboration independence but also topical independence, is still skewed significantly towards collaboration independence (three-quarters of the indicator measure collaboration, while only one-quarter measures topics). Since we consider cognitive/topical independence an important asset of this indicator, we have decided to adjust the formula a bit further and drop the I3 part, to give more weight to the cognitive/topical independence in the whole indicator. Throughout this paper, we will thus refer to the original indicator as RIIo, our adjusted version as RIIa and the part of the indicator measuring only the cognitive independence RIIc.

@@

We used ??? table ??? to estimate the gender of each researcher.

@@

For the construction of the control group, we implemented propensity matching using the package MatchIt (citation?) and matching exactly by the discipline (42 sub-categories of OECD classification), and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant and gender. All of these variables were calculated at the intervention year (i.e. year when the given researcher from experimental group received the Junior Grant). We set caliper to 0.2 standard deviations of the logit of the propensity score by recommendation of Rosenbaum and Rubin (1985b) and Austin (2011) to remove the cases where the distance between experimental and control group observation was too large. __This removed XXXX cases from the experimental group, leaving us with YYY matched observations__. The matching was done in 1:1 ratio and with replacement.

@@

@@

unf_sum <- summary(matched_obj_unfunded, un = FALSE)

summary(matched_obj_unfunded)

@@

cobalt::bal.tab(matched_obj_unfunded, un = FALSE, stats = c("m", "v", "ks"), binary = "std")

cobalt::love.plot(matched_obj_unfunded, binary = "std", var.order = "unmatched")

fun_sum <- summary(matched_obj_funded, un = FALSE)

summary(matched_obj_funded)

@@

>>>>

However, we have made some changes to the indicator. After consulting with its authors, we have changed the aggregation formula to 
$$RII = ((1- I1) + I2 + I3 + I4) / 4$$, since the previous formula had a small error (it weighted I4 double,, i.e. 2*I4). For calculating the share of own research topics of the researcher (I4), we have also not used bibliographic coupling as originally suggested, but text-based topic modelling using publication titles and abstracts. Finally, the original indicator, while tracking not only collaboration independence but also topical independence, is still skewed significantly towards collaboration independence (three-quarters of the indicator measure collaboration, while only one-quarter measures topics). Since we consider cognitive/topical independence an important asset of this indicator, we have decided to adjust the formula a bit further and drop the I3 part, to give more weight to the cognitive/topical independence in the whole indicator. Throughout this paper, we will thus refer to the original indicator as RIIo, our adjusted version as RIIa and the part of the indicator measuring only the cognitive independence RIIc.

---> popsat víc jak počítám topic model??

@@

We used Genderize.io API to estimate the probability of perceived gender based on the first names of researchers. Where available, information about the nationality of researchers was included in the API call to improve accuracy.

@@

For the construction of the control group, we implemented propensity matching using the package MatchIt (citation?) and matching exactly by the discipline (42 sub-categories of OECD classification), and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant and gender. All of these variables were calculated at the intervention year (i.e. year when the given researcher from experimental group received the Junior Grant). The distance was set to "mahalanobis". The matching was done in 1:1 ratio and with replacement.

@@

After matching, all standardized mean differences for the covariates were below 0.1 and all standardized mean differences for squares and two-way interactions between covariates were below .15, indicating adequate balance. __This removed XXXX cases from the experimental group, leaving us with YYY matched observations__.

@@

unf_sum <- summary(tar_read(matched_obj_unfunded), un = TRUE)

summary(tar_read(matched_obj_unfunded))

@@

cobalt::bal.tab(tar_read(matched_obj_unfunded), un = FALSE, stats = c("m", "v", "ks"), binary = "std")

cobalt::love.plot(tar_read(matched_obj_unfunded), binary = "std", var.order = "adjusted")

fun_sum <- summary(tar_read(matched_obj_funded), un = TRUE)

summary(tar_read(matched_obj_funded))

@@

To estimate the treatment effect and its standard error, we fit a linear regression model with 1978 earnings as the outcome and the treatment, covariates, and their interaction as predictors and included the full matching weights in the estimation. The lm() function was used to fit the outcome, and the comparisons() function in the marginaleffects package was used to perform g-computation in the matched sample to estimate the ATT. A cluster-robust variance was used to estimate its standard error with matching stratum membership as the clustering variable.

The estimated effect was XXXX (SE = XXXX, p = XXXX), indicating that the average effect of the treatment for those who received it is to increase earnings.

# Run regression model with interaction term
did_model <- plm(researcher_independence ~ independence_timing * treatment + factor(subclass), 
                 data = tar_read(full_indicator), 
                 index = c("subclass", "independence_timing"),
                 model = "within")

# Calculate clustered standard errors
clustered_se <- coeftest(did_model, vcov = function(x) vcovHC(x, type = "HC1", cluster = "group"))
print(clustered_se)
